A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex
Convention formatting

 Cloud instances hosted a single Dask or Spark worker, configured to use 8 CPUs. We
 used Dask's default configuration that uses all the available memory on the
 instance. Its default heuristic is to: target a 60\% memory load, spill to disk at
 70\%, pause the worker at 80\%, and terminate the worker at 95\%. We configured
 Spark to use 1 executor per worker and \SI{25}{\giga\byte} of memory per executor, to leave 5~GB
 for off-heap. We configured the Spark driver to use 25~GB of memory, and used the
 default configuration for the master. We used the default configuration for worker
 memory management: at 60\% it spills data to disk, and 50\% of that amount is
 reserved for storage that is immune to eviction.

@@

We used BigBrain~\cite{Amunts:13}, a three-dimensional image of a human
brain with voxel intensities ranging from 0 to 65,535. The original data is
stored in 125 blocks in the MINC~\cite{minc} HDF5-based format, available
at \url{ftp://bigbrain.loris.ca/BigBrainRelease.2015/3D\_Blocks/40um} at a
resolution of \SI{40}{\micro\metre}. We converted the blocks into the
\href{https://nifti.nimh.nih.gov/nifti-1}{NifTI} format, a popular format
in neuroimaging. We left the NifTI blocks uncompressed, resulting in 
a total data size of \SI{81}{\giga\byte}. 
To evaluate the effect of block size, we resplit these blocks into 30, 125 and 750 blocks of 
\SI{2.7}{\giga\byte}, \SI{0.648}{\giga\byte}, and
\SI{0.108}{\giga\byte}, using the \href{https://github.com/big-data-lab-team/sam}{sam} library.

@@

%% Incrementation
\subsubsection{Incrementation}
We used an adaptation of the image incrementation pipeline used
in~\cite{hayot2019performance} (see Algorithm~\ref{alg:incrementation}).
The application reads blocks of the BigBrain image from the shared file
system, increments the intensity value of each voxel by 1 to avoid caching
effects, sleeps for a configurable amount of time to emulate more
compute-intensive processing, repeats this process for a specified number of
iterations, and
finally writes the result as a NifTI image back to the shared file system.
This application allows us to study the behaviour of the engines when all
inputs are processed independently, in a map-only scenario (see
Figure~\ref{fig:tg-inc}). This mimics the behaviour of analyzing multiple
independent subjects in parallel.

>>>>

 Cloud instances hosted a single Dask or Spark worker, configured to use 8 CPUs. We
 used Dask's default configuration that uses all the available memory on the
 instance. Its default heuristic is to: target a 60\% memory load, spill to disk at
 70\%, pause the worker at 80\%, and terminate the worker at 95\%. We configured
 Spark to use 1 executor per worker and \SI{25}{\giga\byte} of memory per executor, to leave \SI{5}{\giga\byte}
 for off-heap. We configured the Spark driver to use \SI{25}{\giga\byte} of memory, and used the
 default configuration for the master. We used the default configuration for worker
 memory management: at 60\% it spills data to disk, and 50\% of that amount is
 reserved for storage that is immune to eviction.

@@

We used BigBrain~\cite{Amunts:13}, a three-dimensional image of a human
brain with voxel intensities ranging from 0 to 65,535. The original data is
stored in 125 blocks in the MINC~\cite{minc} HDF5-based format, available
at \url{ftp://bigbrain.loris.ca/BigBrainRelease.2015/3D\_Blocks/40um} at a
resolution of \SI{40}{\micro\metre}. We converted the blocks into the
\href{https://nifti.nimh.nih.gov/nifti-1}{NIfTI} format, a popular format
in neuroimaging. We left the NIfTI blocks uncompressed, resulting in 
a total data size of \SI{81}{\giga\byte}. 
To evaluate the effect of block size, we resplit these blocks into 30, 125 and 750 blocks of 
\SI{2.7}{\giga\byte}, \SI{0.648}{\giga\byte}, and
\SI{0.108}{\giga\byte}, using the \href{https://github.com/big-data-lab-team/sam}{sam} library.

@@

%% Incrementation
\subsubsection{Incrementation}
We used an adaptation of the image incrementation pipeline used
in~\cite{hayot2019performance} (see Algorithm~\ref{alg:incrementation}).
The application reads blocks of the BigBrain image from the shared file
system, increments the intensity value of each voxel by 1 to avoid caching
effects, sleeps for a configurable amount of time to emulate more
compute-intensive processing, repeats this process for a specified number of
iterations, and
finally writes the result as a NIfTI image back to the shared file system.
This application allows us to study the behaviour of the engines when all
inputs are processed independently, in a map-only scenario (see
Figure~\ref{fig:tg-inc}). This mimics the behaviour of analyzing multiple
independent subjects in parallel.
